Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-23 writeups/dissertation/dissertation.tex
foo

To better illustrate the dynamics of each user's tagging behavior,
profile plots for a single user for both StackOverflow and Twitter are included in Figure \ref{figHTByTime}.

\begin{figure}[!htbp]
  {%
    \setlength{\fboxsep}{0pt}%
    \setlength{\fboxrule}{1pt}%
    \hfill
    \subfigure[][StackOverflow]{\includegraphics[width=8cm]{HTByTime-520957-crop.pdf}}
    \hfill
    \subfigure[][Twitter]{\includegraphics[width=8cm]{HTByTime-fashionista_com-crop.pdf}}
    \caption{Tagging profile for a single user}
    \label{figHTByTime}
  }%
\end{figure}

@@

As a first method for understanding model performance, profile plots of model's predicted tags for individual users were overlaid on that user's actual tag use.
These plots for StackOverflow and Twitter are included in Figures \ref{figHTMByTime-520957} and \ref{figHTMByTime-fashionista_com} respectively.
These are the same plots shown in Figure \ref{figHTByTime} with model predictions overlaid in red.

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{HTMByTime-520957-crop.pdf}}}
  \caption{Model tagging profile of a single user on StackOverflow}
  \label{figHTMByTime-520957}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{HTMByTime-fashionista_com-crop.pdf}}}
  \caption{Model tagging profile of a single user on Twitter}
  \label{figHTMByTime-fashionista_com}
\end{figure}

@@

The same previously-derived stoplist from FIXME that \textcite{Sahlgren2008} used was used for this analysis,
The same entropy weighting method using by \textcite{Stanley2013} was examined,
and the same method of removing the high-frequency words from \citeauthor{Sahlgren2008} was used.

@@

The plots for the standard deviations across tags that was used to identify the cutoff for StackOverflow and Twitter are included in Figures \ref{figContextCutoffSO} and \ref{figContextCuttoffT}.

FIXME:

The no-removal plot shows the size of the spikes when high-frequency words are removed.
The entropy plot shows how the size decreases by more than an order of magnitude when the entropy weighting measure is used.
The cutoff was chosen such that the frequency plot looks similar to the entropy plot, with spikes around the same size.
Note that using a previously-defined stoplist does not remove some of the remaining high-frequency words in these datasets, which hints that this method may not be ideal when model accuracy is examined.
The cutoff that produced the frequency plot is where a word represents more than \num{.0004} occurrences in the dataset.
This may or may not be equal to the value for \textcite{Sahlgren2008}, since that number was expressed in total observations (not as a percentage), and the total number of words in the dataset were not given.

@@

Model accuracy as a function of co-occurrence matrix size for StackOverflow is included in Figure \ref{figContextDSizeSO}.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-dimBySizeSO-crop.pdf}}}
  \caption{Effect of size of co-occurrence matrix for StackOverflow}
  \label{figContextDSizeSO}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-dimBySizeSO-crop.pdf}}}
  \caption{Effect of size of co-occurrence matrix for Twitter}
  \label{figContextDSizeSO}
\end{figure}

Both entropy weighting and frequency filtering in Figure \ref{figContextDSizeSO} plateau for the random-permutation model with increasing document size.
Once again, the Bayesian model continues to improve with document size.

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-logoddsSO-crop.pdf}}}
  \caption{Random-permutation model accuracy when using log-odds transformation on context for Twitter}
  \label{figContextLogoddsT}
\end{figure}

>>>>

To better illustrate the dynamics of each user's tagging behavior,
profile plots for a single user for both StackOverflow and Twitter are included in Figure \ref{figPriorHTByTime}.

\begin{figure}[!htbp]
  {%
    \setlength{\fboxsep}{0pt}%
    \setlength{\fboxrule}{1pt}%
    \hfill
    \subfigure[][StackOverflow]{\includegraphics[width=8cm]{HTByTime-520957-crop.pdf}}
    \hfill
    \subfigure[][Twitter]{\includegraphics[width=8cm]{HTByTime-fashionista_com-crop.pdf}}
    \caption{Tagging profile for a single user}
    \label{figPriorHTByTime}
  }%
\end{figure}

@@

As a first method for understanding model performance, profile plots of model's predicted tags for individual users were overlaid on that user's actual tag use.
These plots for StackOverflow and Twitter are included in Figures \ref{figPriorHTMByTimeSO} and \ref{figPriorHTMByTimeT} respectively.
These are the same plots shown in Figure \ref{figPriorHTByTime} with model predictions overlaid in red.

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{HTMByTime-520957-crop.pdf}}}
  \caption{Model tagging profile of a single user on StackOverflow}
  \label{figPriorHTMByTimeSO}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{HTMByTime-fashionista_com-crop.pdf}}}
  \caption{Model tagging profile of a single user on Twitter}
  \label{figPriorHTMByTimeT}
\end{figure}

@@

The same previously-derived stoplist from \textcite{Salton2014} that \textcite{Sahlgren2008} used was used for this analysis,
The same entropy weighting method using by \textcite{Stanley2013} was examined,
and the same method of removing the high-frequency words from \citeauthor{Sahlgren2008} was used.

@@

The plots for the standard deviations across tags that were used to identify the cutoff for StackOverflow and Twitter are included in Figures \ref{figContextCutoffSO} and \ref{figContextCutoffT}.

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{memMatSO-crop.pdf}}}
  \caption{Variance in observation counts of words for each tag for StackOverflow}
  \label{figContextCutoffSO}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{memMatT-crop.pdf}}}
  \caption{Variance in observation counts of words for each tag for Twitter}
  \label{figContextCutoffT}
\end{figure}

The original plot shows the size of the spikes when high-frequency words are removed.
The entropy plot shows how the size decreases by more than an order of magnitude when the entropy weighting measure is used.
The cutoff was chosen such that the frequency plot looks similar to the entropy plot, with spikes around the same size.
Note that using a previously-defined stoplist does not remove some of the remaining high-frequency words in these datasets, which hints that this method may not be ideal when model accuracy is examined.
The cutoff that produced the frequency plot is where a word represents more than \num{.04}\% of total occurrences in the dataset.
This may or may not be equal to the value for \textcite{Sahlgren2008}, since that number was expressed in total observations (not as a percentage), and the total number of words in the dataset was not given.

@@

Model accuracy as a function of co-occurrence matrix size for StackOverflow is included in Figure \ref{figContextDocumentSizeSO}.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-freqVsEntropyBySizeSO-crop.pdf}}}
  \caption{Effect of size of co-occurrence matrix for StackOverflow}
  \label{figContextDocumentSizeSO}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-freqVsEntropyBySizeT-crop.pdf}}}
  \caption{Effect of size of co-occurrence matrix for Twitter}
  \label{figContextDocumentSizeT}
\end{figure}

Both entropy weighting and frequency filtering in Figure \ref{figContextDocumentSizeT} plateau for the random-permutation model with increasing document size.
Once again, the Bayesian model continues to improve with document size.

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-logoddsT-crop.pdf}}}
  \caption{Random-permutation model accuracy when using log-odds transformation on context for Twitter}
  \label{figContextLogoddsT}
\end{figure}
